The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-03-26 paper.tex
NA is not explained anymore, so better use the full name
period

		The Myrmic DHT runs on top of Kademlia, and introduces the Neighbourhood Authority. This authority issues certificates to nodes that participate in the DHT, but it does not participate in the DHT itself. The NA makes this solution not a fully decentralized one, but its role is a lot smaller than the current Directory Servers. This does not solve the trust issue, but it does solve the scalability issue.

@@

\begin{landscape}
	% Zelfde volgorde als hoofdstukken
	% Deze bij hoofdstuk 5 plaatsen!!!
	% Enkel de rijen met stukjes in tekst (I2P? Salsa?)
	\begin{table}[p]
		\centering
		\include{tbl-currentsystems}
		\caption{A comparison of decentralized peer-to-peer overlay networks}
		\label{tbl:comparison}
	\end{table}
\end{landscape}

>>>>

		The Myrmic DHT runs on top of Kademlia, and introduces the Neighbourhood Authority. This authority issues certificates to nodes that participate in the DHT, but it does not participate in the DHT itself. The Neighbourhood Authority makes this solution not a fully decentralized one, but its role is a lot smaller than the current Directory Servers. This does not solve the trust issue, but it does solve the scalability issue.

@@

\begin{landscape}
	% Zelfde volgorde als hoofdstukken
	% Deze bij hoofdstuk 5 plaatsen!!!
	% Enkel de rijen met stukjes in tekst (I2P? Salsa?)
	\begin{table}[p]
		\centering
		\include{tbl-currentsystems}
		\caption{A comparison of decentralized peer-to-peer overlay networks.}
		\label{tbl:comparison}
	\end{table}
\end{landscape}
